---
title: "describe_SUDs_W1-2"
author: "PNR"
Creation date: "June/24/2020"
Last updated: "August/24/2020"
Updated by: "JSS"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

*--------
*0: Setup*
---------*

**0.0: Install packages needed**
------------------------------**
```{r Install Packages, eval=FALSE, include=FALSE}
#once: 
install.packages('tidyverse')
install.packages("Hmisc") #to read por files
install.packages("haven") #to read por files
install.packages("modeest")
install.packages('memisc') #to read codebooks
install.packages("ggplot2") #to plot 
# install.packages("pandas") #package ‘pandas’ is not available (for R version 4.0.0)
install.packages("rquery") #to merge instruments by wave using SQL functions
install.packages("rqdatatable") #to merge instruments by wave using SQL functions
```

```{r Read Packages}
#every time: 
library(readr)
library(tidyverse)
library(haven)
library(ggplot2)
require("Hmisc")
require("memisc")
library("rquery")
  # https://www.rdocumentation.org/packages/rquery/versions/1.4.4
library(rqdatatable)
```

```{r run script that reads CADD instruments}
#source(read_CADD.Rmd)
```

#JS DONE: create a list variable with the names of our variables of interest (ones you highlighted in spreadsheet)
example: Sam_smoke_vars <- list("var1", "var2")
```{r}
Sam_smoke_vars <- list("cigcrit","cigcrit2","cigpeak","cigcurr","cigfreq1","cigfreq2","cigons","cgrcrit","cgrcrit2","cgrpeak","cgrcurr","cgrfreq1","cgrfreq2","cgrons","pipcrit","pipcrit2","pippeak","pipcurr","pipfreq1","pipfreq2","pipons","chwcrit","chwcrit2","chwpeak","chwcurr","chwfreq1","chwfreq2")
```


#JS TODO: look at this link for how to get descritive stats grouped by a variable using the by() function & how to graph based on groups:
https://towardsdatascience.com/descriptive-statistics-in-r-8e1cad20bf3a



-----------------------------
  *1: Read in datasets*
------------------------------


*-------------------------------------------------------------
*4: Descriptives for WHOLE sample (parents, siblings, probands)*
--------------------------------------------------------------*

**1.1: Total Number of People
------------------------------**
Wave 1
-------
```{r}
length(W1_Sam$iid)
#10,432 individuals

length(W1_all$iid)
```

Wave 2
-------
```{r}
length(W2_Sam$iid)
#6,660 individuals
```

**1.2: Total Number of Families
------------------------------**
Wave 1
-------
```{r}
length(unique(W1_Sam$family))
#4,294 families
```

Wave 2
-------
```{r}
length(unique(W2_Sam$family))
#2,890 families
```


*-------------------------------------------------------------
*5: Descriptives for CHILDREN (siblings & probands only)*
--------------------------------------------------------------*

**2.2: Total children
------------------------------**
JS DONE: get total number of children by gettting length of the child subset
```{r}
length(Sam_1_child$iid)
#1,848 children (probands and siblings)
```


**2.3: Age of children
------------------------------**

------------------------
Descriptives for SAM_W1
------------------------

JS DONE: Get range, mean, standard deviation, and median for age of children: 
```{r}
summary(Sam_1_child$nage)
sd(Sam_1_child$nage)
#min age: 10.96 
#median age: 16.58 
#mean age: 16.93
#max age: 35.44
#sd: 3.14
#JS DONE: name these histograms like this: hist_W1_Sam_child : typeofplot_wave_instrument_datasubset 
```

#cigcrit (Ever smoked cigarettes almost every day for at least a month? 0=didn't meet criterion, 1=met criterion)
```{r}
W1_Sam_child$nsex <- factor(W1_Sam_child$nsex) 
W1_Sam_child$nsex <- fct_recode(W1_Sam_child$nsex, "female" = "0", "male" = "1")
summary(W1_Sam_child$cigcrit)
sd(W1_Sam_child$cigcrit)
#min: 0
#median: 0
#mean: 0.44
#max: 1
#sd: 0.50
hist_W1_child_cigcrit<- ggplot(W1_Sam_child, aes(x=cigcrit))+
  geom_histogram(color="darkslategrey",fill="plum") +
  facet_wrap(~nsex) +
  labs(title = "W1 CIDI-SAM Child Cigarette Criteria by Sex") +
  labs(x="CigCrit", y="Count")
hist_W1_child_cigcrit
```
#cigcrit2 (Smoked 20 cigarettes lifetime? 0=didn't meet criterion, 1=met criterion)
```{r}
summary(W1_Sam_child$cigcrit2)
sd(W1_Sam_child$cigcrit2)
#NA for all
```
#cigpeak (How many cigarettes smoked per day when you were smoking most?)
```{r}
summary(W1_Sam_child$cigpeak)
sd(W1_Sam_child$cigpeak)
#min: 1
#median: 20
#mean: 18
#max: 96
#sd: NA
hist_W1_child_cigpeak_sex <- ggplot(W1_Sam_child, aes(x=cigpeak))+
  geom_histogram(color="darkslategrey",fill="plum") +
  facet_wrap(~nsex) +
  labs(title = "W1 CIDI-SAM Child Cigarette Peak by Sex") +
  labs(x="CigPeak", y="Count")
hist_W1_child_cigpeak_sex
```
#cigcurr (In past 12 months, how many cigarettes usually smoked per day?)
```{r}
summary(W1_Sam_child$cigcurr)
sd(W1_Sam_child$cigcurr)
#NA for all
```
#cigfreq1 (Usual frequency of cigarette smoking in past 12 months)
```{r}
summary(W1_Sam_child$cigfreq1)
sd(W1_Sam_child$cigfreq1)
#NA for all
```
#cigfreq2 (Usual frequency of cigarette smoking when smoking most)
```{r}
summary(W1_Sam_child$cigfreq2)
sd(W1_Sam_child$cigfreq2)
#NA for all
```
#cigons (How old were you when you began smoking?)
```{r}
summary(W1_Sam_child$cigons)
sd(W1_Sam_child$cigons)
#min: 5
#median: 13
#mean: 12.58
#max: 26
#sd: NA
hist_W1_child_cigons_sex <- ggplot(W1_Sam_child, aes(x=cigons))+
  geom_histogram(color="darkslategrey",fill="plum") +
  facet_wrap(~nsex) +
  labs(title = "W1 CIDI-SAM Child Cigarette Onset by Sex") +
  labs(x="CigOns", y="Count")
hist_W1_child_cigons_sex
```
#cgrcrit (Ever smoked cigars almost every day for at least a month?)
```{r}
summary(W1_Sam_child$cgrcrit)
sd(W1_Sam_child$cgrcrit)
#min: 0
#median: 0
#mean: 0.03
#max: 1
#sd: 0.17
hist_W1_child_cgrcrit_sex <- ggplot(W1_Sam_child, aes(x=cgrcrit))+
  geom_histogram(color="darkslategrey",fill="plum") +
  facet_wrap(~nsex) +
  labs(title = "W1 CIDI-SAM Child Cigar Criteria by Sex") +
  labs(x="CgrCrit", y="Count")
hist_W1_child_cgrcrit_sex
```
#cgrcrit2 (Smoked more than 5 cigars in your life?)
```{r}
summary(W1_Sam_child$cgrcrit2)
sd(W1_Sam_child$cgrcrit2)
#NA for all
```
#cgrpeak (How many cigars did you smoke per day when you were smoking most?)
```{r}
summary(W1_Sam_child$cgrpeak)
sd(W1_Sam_child$cgrpeak)
#min: 1
#median: 2
#mean: 2.76
#max: 10
#sd: NA
hist_W1_child_cgrpeak_sex <- ggplot(W1_Sam_child, aes(x=cgrpeak))+
  geom_histogram(color="darkslategrey",fill="plum") +
  facet_wrap(~nsex) +
  labs(title = "W1 CIDI-SAM Child Cigar Peak by Sex") +
  labs(x="CgrPeak", y="Count")
hist_W1_child_cgrpeak_sex
```
#cgrcurr (In past 12 months, how many cigars usually smoked in a day?)
```{r}
summary(W1_Sam_child$cgrcurr)
sd(W1_Sam_child$cgrcurr)
#NA for all
```
#cgrfreq1 (Usual frequency of cigar smoking in past 12 months)
```{r}
summary(W1_Sam_child$cgrfreq1)
sd(W1_Sam_child$cgrfreq1)
#NA for all
```
#cgrfreq2 (Usual frequency of cigar smoking in period of heaviest cigar smoking)
```{r}
summary(W1_Sam_child$cgrfreq2)
sd(W1_Sam_child$cgrfreq2)
#NA for all
```
#cgrons (How old were you when you began smoking cigars?)
```{r}
summary(W1_Sam_child$cgrons)
sd(W1_Sam_child$cgrons)
#min: 10
#median: 15
#mean: 14.49
#max: 18
#sd: NA
hist_W1_child_cgrons_sex <- ggplot(W1_Sam_child, aes(x=cgrons))+
  geom_histogram(color="darkslategrey",fill="plum") +
  facet_wrap(~nsex) +
  labs(title = "W1 CIDI-SAM Child Cigar Onset by Sex") +
  labs(x="CgrOns", y="Count")
hist_W1_child_cgrons_sex
```
#pipcrit (Ever smoked a pipe almost every day for at least a month?)
```{r}
summary(W1_Sam_child$pipcrit)
sd(W1_Sam_child$pipcrit)
#min: 0
#median: 0
#mean: 0.008
#max: 1
#sd: 0.09
hist_W1_child_pipcrit_sex <- ggplot(W1_Sam_child, aes(x=pipcrit))+
  geom_histogram(color="darkslategrey",fill="plum") +
  facet_wrap(~nsex) +
  labs(title = "W1 CIDI-SAM Child Pipe Criteria by Sex") +
  labs(x="PipCrit", y="Count")
hist_W1_child_pipcrit_sex
```
#pipcrit2 (Smoked tobacco in a pipe more than 5 times in your life?)
```{r}
summary(W1_Sam_child$pipcrit2)
sd(W1_Sam_child$pipcrit2)
#NA for all
```
#pippeak (How many pipefuls of tobacco per day when you were smoking most?)
```{r}
summary(W1_Sam_child$pippeak)
sd(W1_Sam_child$pippeak)
#min: 1
#median: 2
#mean: 5.357
#max: 30
#sd: NA
hist_W1_child_pippeak_sex <- ggplot(W1_Sam_child, aes(x=pippeak))+
  geom_histogram(color="darkslategrey",fill="plum") +
  facet_wrap(~nsex) +
  labs(title = "W1 CIDI-SAM Child Pipe Peak by Sex") +
  labs(x="PipPeak", y="Count")
hist_W1_child_pippeak_sex
```
#pipcurr (IN past 12 months, how many pipefuls smoked in a day?)
```{r}
summary(W1_Sam_child$pipcurr)
sd(W1_Sam_child$pipcurr)
#NA for all
```
#pipfreq1 (Usual frequency of pipe smoking in past 12 months)
```{r}
summary(W1_Sam_child$pipfreq1)
sd(W1_Sam_child$pipfreq1)
#NA for all
```
#pipfreq2 (Usual frequency of pipe smoking in period of heaviest pipe smoking)
```{r}
summary(W1_Sam_child$pipfreq2)
sd(W1_Sam_child$pipfreq2)
#NA for all
```
#pipons (How old were you when you began to smoke a pipe?)
```{r}
summary(W1_Sam_child$pipons)
sd(W1_Sam_child$pipons)
#min: 8
#median: 14.5
#mean: 14.5
#max: 19
#sd: NA
hist_W1_child_pipons_sex <- ggplot(W1_Sam_child, aes(x=pipons))+
  geom_histogram(color="darkslategrey",fill="plum") +
  facet_wrap(~nsex) +
  labs(title = "W1 CIDI-SAM Child Pipe Onset by Sex") +
  labs(x="PipOns", y="Count")
hist_W1_child_pipons_sex
```
#chwcrit (Have you ever used snuff or chewed tobacco {ALMOST EVERY DAY FOR AT LEAST A MONTH}?)
```{r}
summary(W1_Sam_child$chwcrit)
sd(W1_Sam_child$chwcrit)
#min: 0
#median: 0
#mean: 0.11
#max: 1
#sd: 0.31
hist_W1_child_chwcrit_sex <- ggplot(W1_Sam_child, aes(x=chwcrit))+
  geom_histogram(color="darkslategrey",fill="plum") +
  facet_wrap(~nsex) +
  labs(title = "W1 CIDI-SAM Child Chewing Tobacco Criteria by Sex") +
  labs(x="ChwCrit", y="Count")
hist_W1_child_chwcrit_sex
```
#chwcrit2 (Used snuff or chewed tobacco more than 5 times in your life?)
```{r}
summary(W1_Sam_child$chwcrit2)
sd(W1_Sam_child$chwcrit2)
#NA for all
```
#chwpeak (How many pouches of snuff/chews per day when you were using most?)
```{r}
summary(W1_Sam_child$chwpeak)
sd(W1_Sam_child$chwpeak)
#min: 0.5
#median: 1
#mean: 2.97
#max: 40
#sd: NA
hist_W1_child_chwpeak_sex <- ggplot(W1_Sam_child, aes(x=chwpeak))+
  geom_histogram(color="darkslategrey",fill="plum") +
  facet_wrap(~nsex) +
  labs(title = "W1 CIDI-SAM Child Chewing Tobacco Peak by Sex") +
  labs(x="ChwPeak", y="Count")
hist_W1_child_chwpeak_sex
```
#chwcurr (In past 12 months, how many pouches of snuff or chews used per day?)
```{r}
summary(W1_Sam_child$chwcurr)
sd(W1_Sam_child$chwcurr)
#NA for all
```
#chwfreq1 (Usual frequency of snuff/chew in past 12 months)
```{r}
summary(W1_Sam_child$chwfreq1)
sd(W1_Sam_child$chwfreq1)
#NA for all
```
#chwfreq2 (Usual frequency of snuff/chew during period of heaviest use)
```{r}
summary(W1_Sam_child$chwfreq2)
sd(W1_Sam_child$chwfreq2)
#NA for all
```
#chwons (How old were you when you began using tobacco or snuff?)
```{r}
summary(W1_Sam_child$chwons)
sd(W1_Sam_child$chwons)
#min: 5
#median: 14
#mean: 13.91
#max: 21
#sd: NA
hist_W1_child_chwons_sex <- ggplot(W1_Sam_child, aes(x=chwons))+
  geom_histogram(color="darkslategrey",fill="plum") +
  facet_wrap(~nsex) +
  labs(title = "W1 CIDI-SAM Child Chewing Tobacco Onset by Sex") +
  labs(x="ChwOns", y="Count")
hist_W1_child_chwons_sex
```

*-------------------------------------------------------------
  *6: Descriptives for PROBANDS (probands only)*
---------------------------------------------------------------
Histograms for each Variable
#CIDI-SAM Supplement
```{r}
#
hist_W1_Supps_proband <- ggplot(W1_Supps_proband, aes(x=))+
  geom_histogram(color="grey31",fill="darkseagreen2")+
  facet_wrap(~NAGE)+
  labs(title="W1 CIDI-SAM Proband ")
```

```{r}
```

```{r}
```

```{r}

```


**3.1: Total Probands
------------------------------**
JS DONE: get total number of children by getting length of the probands subset
```{r}
length(Sam_1_proband$iid)
#1,008 probands
```

**3.2: Age of probands
------------------------------**
JS DONE: Get range, mean, standard deviation, and median for age of probands: 
```{r}
summary(Sam_1_proband$nage)
sd(Sam_1_proband$nage)
#min age: 11.66
#median age: 16.44
#mean age: 16.37
#max age: 21.05
#sd: 1.33
```

**3.3: SAM_W1 Proband Descriptives
-------------------------------**
PROBAND USERS
#cigcrit
```{r}
summary(W1_Sam_prob_users$cigcrit)
sd(W1_Sam_prob_users)$cigcrit)
#min: 0
#median: 0
#mean: 0.44
#max: 1
#sd: 0.50
hist_W1_proband_cigcrit<- ggplot(W1_Sam_proband, aes(x=cigcrit))+
  geom_histogram(color="darkslategrey",fill="cyan3") +
  facet_wrap(~nsex) +
  labs(title = "W1 CIDI-SAM Proband Cigarette Criteria by Sex") +
  labs(x="CigCrit", y="Count")
hist_W1_proband_cigcrit
```
#cigcrit2
```{r}
summary(W1_Sam_child$cigcrit2)
sd(W1_Sam_child$cigcrit2)
#NA for all
```
#cigpeak
```{r}
summary(W1_Sam_child$cigpeak)
sd(W1_Sam_child$cigpeak)
#min: 1
#median: 20
#mean: 18
#max: 96
#sd: NA
hist_W1_proband_cigpeak<- ggplot(W1_Sam_proband, aes(x=cigpeak))+
  geom_histogram(color="darkslategrey",fill="cyan3") +
  facet_wrap(~nsex) +
  labs(title = "W1 CIDI-SAM Proband Cigarette Peak by Sex") +
  labs(x="CigPeak", y="Count")
hist_W1_proband_cigpeak
```
#cigcurr
```{r}
summary(W1_Sam_child$cigcurr)
sd(W1_Sam_child$cigcurr)
#NA for all
```
#cigfreq1
```{r}
summary(W1_Sam_child$cigfreq1)
sd(W1_Sam_child$cigfreq1)
#NA for all
```
#cigfreq2
```{r}
summary(W1_Sam_child$cigfreq2)
sd(W1_Sam_child$cigfreq2)
#NA for all
```
#cigons
```{r}
summary(W1_Sam_child$cigons)
sd(W1_Sam_child$cigons)
#min: 5
#median: 13
#mean: 12.58
#max: 26
#sd: NA
hist_W1_proband_cigons<- ggplot(W1_Sam_proband, aes(x=cigons))+
  geom_histogram(color="darkslategrey",fill="cyan3") +
  facet_wrap(~nsex) +
  labs(title = "W1 CIDI-SAM Proband Cigarette Onset by Sex") +
  labs(x="CigOns", y="Count")
hist_W1_proband_cigons
```
#cgrcrit
```{r}
summary(W1_Sam_child$cgrcrit)
sd(W1_Sam_child$cgrcrit)
#min: 0
#median: 0
#mean: 0.03
#max: 1
#sd: 0.17
hist_W1_proband_cgrcrit<- ggplot(W1_Sam_proband, aes(x=cgrcrit))+
  geom_histogram(color="darkslategrey",fill="cyan3") +
  facet_wrap(~nsex) +
  labs(title = "W1 CIDI-SAM Proband Cigar Criteria by Sex") +
  labs(x="CgrCrit", y="Count")
hist_W1_proband_cgrcrit
```
#cgrcrit2
```{r}
summary(W1_Sam_child$cgrcrit2)
sd(W1_Sam_child$cgrcrit2)
#NA for all
```
#cgrpeak
```{r}
summary(W1_Sam_child$cgrpeak)
sd(W1_Sam_child$cgrpeak)
#min: 1
#median: 2
#mean: 2.76
#max: 10
#sd: NA
hist_W1_proband_cgrpeak<- ggplot(W1_Sam_proband, aes(x=cgrpeak))+
  geom_histogram(color="darkslategrey",fill="cyan3") +
  facet_wrap(~nsex) +
  labs(title = "W1 CIDI-SAM Proband Cigar Peak by Sex") +
  labs(x="CgrPeak", y="Count")
hist_W1_proband_cgrpeak
```
#cgrcurr
```{r}
summary(W1_Sam_child$cgrcurr)
sd(W1_Sam_child$cgrcurr)
#NA for all
```
#cgrfreq1
```{r}
summary(W1_Sam_child$cgrfreq1)
sd(W1_Sam_child$cgrfreq1)
#NA for all
```
#cgrfreq2
```{r}
summary(W1_Sam_child$cgrfreq2)
sd(W1_Sam_child$cgrfreq2)
#NA for all
```
#cgrons
```{r}
summary(W1_Sam_child$cgrons)
sd(W1_Sam_child$cgrons)
#min: 10
#median: 15
#mean: 14.49
#max: 18
#sd: NA
hist_W1_proband_cgrons<- ggplot(W1_Sam_proband, aes(x=cgrons))+
  geom_histogram(color="darkslategrey",fill="cyan3") +
  facet_wrap(~nsex) +
  labs(title = "W1 CIDI-SAM Proband Cigar Onset by Sex") +
  labs(x="CgrOns", y="Count")
hist_W1_proband_cgrons
```
#pipcrit
```{r}
summary(W1_Sam_child$pipcrit)
sd(W1_Sam_child$pipcrit)
#min: 0
#median: 0
#mean: 0.008
#max: 1
#sd: 0.09
hist_W1_proband_pipcrit<- ggplot(W1_Sam_proband, aes(x=pipcrit))+
  geom_histogram(color="darkslategrey",fill="cyan3") +
  facet_wrap(~nsex) +
  labs(title = "W1 CIDI-SAM Proband Pipe Criteria by Sex") +
  labs(x="PipCrit", y="Count")
hist_W1_proband_pipcrit
```
#pipcrit
```{r}
summary(W1_Sam_child$pipcrit2)
sd(W1_Sam_child$pipcrit2)
#NA for all
```
#pippeak
```{r}
summary(W1_Sam_child$pippeak)
sd(W1_Sam_child$pippeak)
#min: 1
#median: 2
#mean: 5.357
#max: 30
#sd: NA
hist_W1_proband_pippeak<- ggplot(W1_Sam_proband, aes(x=pippeak))+
  geom_histogram(color="darkslategrey",fill="cyan3") +
  facet_wrap(~nsex) +
  labs(title = "W1 CIDI-SAM Proband Pipe Peak by Sex") +
  labs(x="PipPeak", y="Count")
hist_W1_proband_pippeak
```
#pipcurr
```{r}
summary(W1_Sam_child$pipcurr)
sd(W1_Sam_child$pipcurr)
#NA for all
```
#pipfreq1
```{r}
summary(W1_Sam_child$pipfreq1)
sd(W1_Sam_child$pipfreq1)
#NA for all
```
#pipfreq2
```{r}
summary(W1_Sam_child$pipfreq2)
sd(W1_Sam_child$pipfreq2)
#NA for all
```
#pipons
```{r}
summary(W1_Sam_child$pipons)
sd(W1_Sam_child$pipons)
#min: 8
#median: 14.5
#mean: 14.5
#max: 19
#sd: NA
hist_W1_proband_pipons<- ggplot(W1_Sam_proband, aes(x=pipons))+
  geom_histogram(color="darkslategrey",fill="cyan3") +
  facet_wrap(~nsex) +
  labs(title = "W1 CIDI-SAM Proband Pipe Onset by Sex") +
  labs(x="PipOns", y="Count")
hist_W1_proband_pipons
```
#chwcrit
```{r}
summary(W1_Sam_child$chwcrit)
sd(W1_Sam_child$chwcrit)
#min: 0
#median: 0
#mean: 0.11
#max: 1
#sd: 0.31
hist_W1_proband_chwcrit<- ggplot(W1_Sam_proband, aes(x=chwcrit))+
  geom_histogram(color="darkslategrey",fill="cyan3") +
  facet_wrap(~nsex) +
  labs(title = "W1 CIDI-SAM Proband Chewing Tobacco Criteria by Sex") +
  labs(x="ChwCrit", y="Count")
hist_W1_proband_chwcrit
```
#chwcrit2
```{r}
summary(W1_Sam_child$chwcrit2)
sd(W1_Sam_child$chwcrit2)
#NA for all
```
#chwpeak
```{r}
summary(W1_Sam_child$chwpeak)
sd(W1_Sam_child$chwpeak)
#min: 0.5
#median: 1
#mean: 2.97
#max: 40
#sd: NA
hist_W1_proband_chwpeak<- ggplot(W1_Sam_proband, aes(x=chwpeak))+
  geom_histogram(color="darkslategrey",fill="cyan3") +
  facet_wrap(~nsex) +
  labs(title = "W1 CIDI-SAM Proband Chewing Tobacco Peak by Sex") +
  labs(x="ChwPeak", y="Count")
hist_W1_proband_chwpeak
```
#chwcurr
```{r}
summary(W1_Sam_child$chwcurr)
sd(W1_Sam_child$chwcurr)
#NA for all
```
#chwfreq1
```{r}
summary(W1_Sam_child$chwfreq1)
sd(W1_Sam_child$chwfreq1)
#NA for all
```
#chwfreq2
```{r}
summary(W1_Sam_child$chwfreq2)
sd(W1_Sam_child$chwfreq2)
#NA for all
```
#chwons
```{r}
summary(W1_Sam_child$chwons)
sd(W1_Sam_child$chwons)
#min: 5
#median: 14
#mean: 13.91
#max: 21
#sd: NA
hist_W1_proband_chwons<- ggplot(W1_Sam_proband, aes(x=chwons))+
  geom_histogram(color="darkslategrey",fill="cyan3") +
  facet_wrap(~nsex) +
  labs(title = "W1 CIDI-SAM Proband Chewing Tobacco Onset by Sex") +
  labs(x="Chwons", y="Count")
hist_W1_proband_chwons
```

*-------------------------------------------------------------
*7: Descriptives for PROBAND USERS (probands who SMOKE only)*
--------------------------------------------------------------*
**TEST Descriptives
```{r}
length(W1_Sam_prob_test$ID)
#607 proband test
W1_Sam_prob_test$nsex <- factor(W1_Sam_prob_test$nsex) 
W1_Sam_prob_test$nsex <- fct_recode(W1_Sam_prob_test$nsex, "female" = "0", "male" = "1")
```
#age
```{r}
summary(W1_Sam_prob_test$nage)
sd(W1_Sam_prob_test$nage)
#min: 12.95
#median: 16.36
#mean: 16.30
#max: 19.71
#sd: 1.205723
```
#cigcrit
```{r}
summary(W1_Sam_prob_test$cigcrit)
sd(W1_Sam_prob_test$cigcrit)
#min: 0
#median: 1
#mean: 0.827
#max: 1
#sd: 0.3785435
```
#cigcrit2 (Smoked 20 cigarettes lifetime? 0=didn't meet criterion, 1=met criterion)
```{r}
summary(W1_Sam_prob_test$cigcrit2)
sd(W1_Sam_prob_test$cigcrit2)
#NA for all
```
#cigpeak (How many cigarettes smoked per day when you were smoking most?)
```{r}
summary(W1_Sam_prob_test$cigpeak)
sd(W1_Sam_prob_test$cigpeak)
#min: 1
#median: 20
#mean: 20.21
#max: 80
#sd: NA
```
#cigcurr (In past 12 months, how many cigarettes usually smoked per day?)
```{r}
summary(W1_Sam_prob_test$cigcurr)
sd(W1_Sam_prob_test$cigcurr)
#NA for all
```
#cigfreq1 (Usual frequency of cigarette smoking in past 12 months)
```{r}
summary(W1_Sam_prob_test$cigfreq1)
sd(W1_Sam_prob_test$cigfreq1)
#NA for all
```
#cigfreq2 (Usual frequency of cigarette smoking when smoking most)
```{r}
summary(W1_Sam_prob_test$cigfreq2)
sd(W1_Sam_prob_test$cigfreq2)
#NA for all
```
#cigons (How old were you when you began smoking?)
```{r}
summary(W1_Sam_prob_test$cigons)
sd(W1_Sam_prob_test$cigons)
#min: 5
#median: 12
#mean: 11.88
#max: 17
#sd: NA
```
#cgrcrit (Ever smoked cigars almost every day for at least a month?)
```{r}
summary(W1_Sam_prob_test$cgrcrit)
sd(W1_Sam_prob_test$cgrcrit)
#min: 0
#median: 0
#mean: 0.05931
#max: 1
#sd: 0.2363952
```
#cgrcrit2 (Smoked more than 5 cigars in your life?)
```{r}
summary(W1_Sam_prob_test$cgrcrit2)
sd(W1_Sam_prob_test$cgrcrit2)
#NA for all
```
#cgrpeak (How many cigars did you smoke per day when you were smoking most?)
```{r}
summary(W1_Sam_prob_test$cgrpeak)
sd(W1_Sam_prob_test$cgrpeak)
#min: 1
#median: 3
#mean: 3.171
#max: 10
#sd: NA
```
#cgrcurr (In past 12 months, how many cigars usually smoked in a day?)
```{r}
summary(W1_Sam_prob_test$cgrcurr)
sd(W1_Sam_prob_test$cgrcurr)
#NA for all
```
#cgrfreq1 (Usual frequency of cigar smoking in past 12 months)
```{r}
summary(W1_Sam_prob_test$cgrfreq1)
sd(W1_Sam_prob_test$cgrfreq1)
#NA for all
```
#cgrfreq2 (Usual frequency of cigar smoking in period of heaviest cigar smoking)
```{r}
summary(W1_Sam_prob_test$cgrfreq2)
sd(W1_Sam_prob_test$cgrfreq2)
#NA for all
```
#cgrons (How old were you when you began smoking cigars?)
```{r}
summary(W1_Sam_prob_test$cgrons)
sd(W1_Sam_prob_test$cgrons)
#min: 10
#median: 14
#mean: 14.14
#max: 18
#sd: NA
```
#pipcrit (Ever smoked a pipe almost every day for at least a month?)
```{r}
summary(W1_Sam_prob_test$pipcrit)
sd(W1_Sam_prob_test$pipcrit)
#min: 0
#median: 0
#mean: 0.01318
#max: 1
#sd: 0.1141373
```
#pipcrit2 (Smoked tobacco in a pipe more than 5 times in your life?)
```{r}
summary(W1_Sam_prob_test$pipcrit2)
sd(W1_Sam_prob_test$pipcrit2)
#NA for all
```
#pippeak (How many pipefuls of tobacco per day when you were smoking most?)
```{r}
summary(W1_Sam_prob_test$pippeak)
sd(W1_Sam_prob_test$pippeak)
#min: 1
#median: 6
#mean: 8.125
#max: 30
#sd: NA
```
#pipcurr (IN past 12 months, how many pipefuls smoked in a day?)
```{r}
summary(W1_Sam_prob_test$pipcurr)
sd(W1_Sam_prob_test$pipcurr)
#NA for all
```
#pipfreq1 (Usual frequency of pipe smoking in past 12 months)
```{r}
summary(W1_Sam_prob_test$pipfreq1)
sd(W1_Sam_prob_test$pipfreq1)
#NA for all
```
#pipfreq2 (Usual frequency of pipe smoking in period of heaviest pipe smoking)
```{r}
summary(W1_Sam_prob_test$pipfreq2)
sd(W1_Sam_prob_test$pipfreq2)
#NA for all
```
#pipons (How old were you when you began to smoke a pipe?)
```{r}
summary(W1_Sam_prob_test$pipons)
sd(W1_Sam_prob_test$pipons)
#min: 12
#median: 13
#mean: 13.5
#max: 16
#sd: NA
```
#chwcrit (Have you ever used snuff or chewed tobacco {ALMOST EVERY DAY FOR AT LEAST A MONTH}?)
```{r}
summary(W1_Sam_prob_test$chwcrit)
sd(W1_Sam_prob_test$chwcrit)
#min: 0
#median: 0
#mean: 0.2372
#max: 1
#sd: 0.4257367
```
#chwcrit2 (Used snuff or chewed tobacco more than 5 times in your life?)
```{r}
summary(W1_Sam_prob_test$chwcrit2)
sd(W1_Sam_prob_test$chwcrit2)
#NA for all
```
#chwpeak (How many pouches of snuff/chews per day when you were using most?)
```{r}
summary(W1_Sam_prob_test$chwpeak)
sd(W1_Sam_prob_test$chwpeak)
#min: 0.5
#median: 1
#mean: 2.518
#max: 40
#sd: NA
```
#chwcurr (In past 12 months, how many pouches of snuff or chews used per day?)
```{r}
summary(W1_Sam_prob_test$chwcurr)
sd(W1_Sam_prob_test$chwcurr)
#NA for all
```
#chwfreq1 (Usual frequency of snuff/chew in past 12 months)
```{r}
summary(W1_Sam_prob_test$chwfreq1)
sd(W1_Sam_prob_test$chwfreq1)
#NA for all
```
#chwfreq2 (Usual frequency of snuff/chew during period of heaviest use)
```{r}
summary(W1_Sam_prob_test$chwfreq2)
sd(W1_Sam_prob_test$chwfreq2)
#NA for all
```
#chwons (How old were you when you began using tobacco or snuff?)
```{r}
summary(W1_Sam_prob_test$chwons)
sd(W1_Sam_prob_test$chwons)
#min: 5
#median: 14
#mean: 13.52
#max: 17
#sd: NA
```
**TEST Histograms
#age
```{r}
hist_W1_prob_test_age<- ggplot(W1_Sam_prob_test, aes(x=nage))+
  geom_histogram(color="darkslategrey",fill="cornflowerblue") +
  facet_wrap(~nsex) +
  labs(title = "W1 CIDI-SAM Proband Test Age by Sex") +
  labs(x="Age", y="Count")
hist_W1_prob_test_age
```
#cigcrit
```{r}
hist_W1_prob_test_cigcrit<- ggplot(W1_Sam_prob_test, aes(x=cigcrit))+
  geom_histogram(color="darkslategrey",fill="cornflowerblue") +
  facet_wrap(~nsex) +
  labs(title = "W1 CIDI-SAM Proband Test Cigarette Criteria by Sex") +
  labs(x="cigcrit", y="Count")
hist_W1_prob_test_cigcrit
```
#cigpeak
```{r}
hist_W1_prob_test_cigpeak<- ggplot(W1_Sam_prob_test, aes(x=cigpeak))+
  geom_histogram(color="darkslategrey",fill="cornflowerblue") +
  facet_wrap(~nsex) +
  labs(title = "W1 CIDI-SAM Proband Test Cigarette Peak by Sex") +
  labs(x="cigpeak", y="Count")
hist_W1_prob_test_cigpeak
```
#cigons
```{r}
hist_W1_prob_test_cigons<- ggplot(W1_Sam_prob_test, aes(x=cigons))+
  geom_histogram(color="darkslategrey",fill="cornflowerblue") +
  facet_wrap(~nsex) +
  labs(title = "W1 CIDI-SAM Proband Test Cigarette Onset by Sex") +
  labs(x="cigons", y="Count")
hist_W1_prob_test_cigons
```
#cgrcrit
```{r}
hist_W1_prob_test_cgrcrit<- ggplot(W1_Sam_prob_test, aes(x=cgrcrit))+
  geom_histogram(color="darkslategrey",fill="cornflowerblue") +
  facet_wrap(~nsex) +
  labs(title = "W1 CIDI-SAM Proband Test Cigar Criteria by Sex") +
  labs(x="cgrcrit", y="Count")
hist_W1_prob_test_cgrcrit
```
#cgrpeak
```{r}
hist_W1_prob_test_cgrpeak<- ggplot(W1_Sam_prob_test, aes(x=cgrpeak))+
  geom_histogram(color="darkslategrey",fill="cornflowerblue") +
  facet_wrap(~nsex) +
  labs(title = "W1 CIDI-SAM Proband Test Cigar Peak by Sex") +
  labs(x="cgrpeak", y="Count")
hist_W1_prob_test_cgrpeak
```
#cgrons
```{r}
hist_W1_prob_test_cgrons<- ggplot(W1_Sam_prob_test, aes(x=cgrons))+
  geom_histogram(color="darkslategrey",fill="cornflowerblue") +
  facet_wrap(~nsex) +
  labs(title = "W1 CIDI-SAM Proband Test Cigar Onset by Sex") +
  labs(x="cgrons", y="Count")
hist_W1_prob_test_cgrons
```
#pipcrit
```{r}
hist_W1_prob_test_pipcrit<- ggplot(W1_Sam_prob_test, aes(x=pipcrit))+
  geom_histogram(color="darkslategrey",fill="cornflowerblue") +
  facet_wrap(~nsex) +
  labs(title = "W1 CIDI-SAM Proband Test Pipe Criteria by Sex") +
  labs(x="pipcrit", y="Count")
hist_W1_prob_test_pipcrit
```
#pippeak
```{r}
hist_W1_prob_test_pippeak<- ggplot(W1_Sam_prob_test, aes(x=pippeak))+
  geom_histogram(color="darkslategrey",fill="cornflowerblue") +
  facet_wrap(~nsex) +
  labs(title = "W1 CIDI-SAM Proband Test Pipe Peak by Sex") +
  labs(x="pippeak", y="Count")
hist_W1_prob_test_pippeak
```
#pipons
```{r}
hist_W1_prob_test_pipons<- ggplot(W1_Sam_prob_test, aes(x=pipons))+
  geom_histogram(color="darkslategrey",fill="cornflowerblue") +
  facet_wrap(~nsex) +
  labs(title = "W1 CIDI-SAM Proband Test Pipe Onset by Sex") +
  labs(x="pipons", y="Count")
hist_W1_prob_test_pipons
```
#chwcrit
```{r}
hist_W1_prob_test_chwcrit<- ggplot(W1_Sam_prob_test, aes(x=chwcrit))+
  geom_histogram(color="darkslategrey",fill="cornflowerblue") +
  facet_wrap(~nsex) +
  labs(title = "W1 CIDI-SAM Proband Test Chewing Tobacco Criteria by Sex") +
  labs(x="chwcrit", y="Count")
hist_W1_prob_test_chwcrit
```
#chwpeak
```{r}
hist_W1_prob_test_chwpeak<- ggplot(W1_Sam_prob_test, aes(x=chwpeak))+
  geom_histogram(color="darkslategrey",fill="cornflowerblue") +
  facet_wrap(~nsex) +
  labs(title = "W1 CIDI-SAM Proband Test Chewing Tobacco Peak by Sex") +
  labs(x="chwpeak", y="Count")
hist_W1_prob_test_chwpeak
```
#chwons
```{r}
hist_W1_prob_test_chwons<- ggplot(W1_Sam_prob_test, aes(x=chwons))+
  geom_histogram(color="darkslategrey",fill="cornflowerblue") +
  facet_wrap(~nsex) +
  labs(title = "W1 CIDI-SAM Proband Test Chewing Tobacco Onset by Sex") +
  labs(x="chwons", y="Count")
hist_W1_prob_test_chwons
```

**CONTROL Descriptives
```{r}
length(W1_Sam_prob_control$ID)
#401 proband control
W1_Sam_prob_control$nsex <- factor(W1_Sam_prob_control$nsex) 
W1_Sam_prob_control$nsex <- fct_recode(W1_Sam_prob_control$nsex, "female" = "0", "male" = "1")
```
#age
```{r}
summary(W1_Sam_prob_control$nage)
sd(W1_Sam_prob_control$nage)
#min: 11.66
#median: 16.56
#mean: 16.46
#max: 21.05
#sd: 1.497237
```
#cigcrit
```{r}
summary(W1_Sam_prob_control$cigcrit)
sd(W1_Sam_prob_control$cigcrit)
#min: 0
#median: 0
#mean: 0.1521
#max: 1
#sd: 0.3595855
```
#cigcrit2 (Smoked 20 cigarettes lifetime? 0=didn't meet criterion, 1=met criterion)
```{r}
summary(W1_Sam_prob_control$cigcrit2)
sd(W1_Sam_prob_control$cigcrit2)
#NA for all
```
#cigpeak (How many cigarettes smoked per day when you were smoking most?)
```{r}
summary(W1_Sam_prob_control$cigpeak)
sd(W1_Sam_prob_control$cigpeak)
#min: 1
#median: 10
#mean: 12.25
#max: 45
#sd: NA
```
#cigcurr (In past 12 months, how many cigarettes usually smoked per day?)
```{r}
summary(W1_Sam_prob_control$cigcurr)
sd(W1_Sam_prob_control$cigcurr)
#NA for all
```
#cigfreq1 (Usual frequency of cigarette smoking in past 12 months)
```{r}
summary(W1_Sam_prob_control$cigfreq1)
sd(W1_Sam_prob_control$cigfreq1)
#NA for all
```
#cigfreq2 (Usual frequency of cigarette smoking when smoking most)
```{r}
summary(W1_Sam_prob_control$cigfreq2)
sd(W1_Sam_prob_control$cigfreq2)
#NA for all
```
#cigons (How old were you when you began smoking?)
```{r}
summary(W1_Sam_prob_control$cigons)
sd(W1_Sam_prob_control$cigons)
#min: 9
#median: 14
#mean: 13.5
#max: 17
#sd: NA
```
#cgrcrit (Ever smoked cigars almost every day for at least a month?)
```{r}
summary(W1_Sam_prob_control$cgrcrit)
sd(W1_Sam_prob_control$cgrcrit)
#min: 0
#median: 0
#mean: 0.01247
#max: 1
#sd: 0.1111042
```
#cgrcrit2 (Smoked more than 5 cigars in your life?)
```{r}
summary(W1_Sam_prob_control$cgrcrit2)
sd(W1_Sam_prob_control$cgrcrit2)
#NA for all
```
#cgrpeak (How many cigars did you smoke per day when you were smoking most?)
```{r}
summary(W1_Sam_prob_control$cgrpeak)
sd(W1_Sam_prob_control$cgrpeak)
#min: 1
#median: 1
#mean: 1.2
#max: 2
#sd: NA
```
#cgrcurr (In past 12 months, how many cigars usually smoked in a day?)
```{r}
summary(W1_Sam_prob_control$cgrcurr)
sd(W1_Sam_prob_control$cgrcurr)
#NA for all
```
#cgrfreq1 (Usual frequency of cigar smoking in past 12 months)
```{r}
summary(W1_Sam_prob_control$cgrfreq1)
sd(W1_Sam_prob_control$cgrfreq1)
#NA for all
```
#cgrfreq2 (Usual frequency of cigar smoking in period of heaviest cigar smoking)
```{r}
summary(W1_Sam_prob_control$cgrfreq2)
sd(W1_Sam_prob_control$cgrfreq2)
#NA for all
```
#cgrons (How old were you when you began smoking cigars?)
```{r}
summary(W1_Sam_prob_control$cgrons)
sd(W1_Sam_prob_control$cgrons)
#min: 12
#median: 14
#mean: 14.4
#max: 17
#sd: NA
```
#pipcrit (Ever smoked a pipe almost every day for at least a month?)
```{r}
summary(W1_Sam_prob_control$pipcrit)
sd(W1_Sam_prob_control$pipcrit)
#min: 0
#median: 0
#mean: 0.009975
#max: 1
#sd: 0.0995
```
#pipcrit2 (Smoked tobacco in a pipe more than 5 times in your life?)
```{r}
summary(W1_Sam_prob_control$pipcrit2)
sd(W1_Sam_prob_control$pipcrit2)
#NA for all
```
#pippeak (How many pipefuls of tobacco per day when you were smoking most?)
```{r}
summary(W1_Sam_prob_control$pippeak)
sd(W1_Sam_prob_control$pippeak)
#min: 1
#median: 1
#mean: 1.333
#max: 2
#sd: NA
```
#pipcurr (IN past 12 months, how many pipefuls smoked in a day?)
```{r}
summary(W1_Sam_prob_control$pipcurr)
sd(W1_Sam_prob_control$pipcurr)
#NA for all
```
#pipfreq1 (Usual frequency of pipe smoking in past 12 months)
```{r}
summary(W1_Sam_prob_control$pipfreq1)
sd(W1_Sam_prob_control$pipfreq1)
#NA for all
```
#pipfreq2 (Usual frequency of pipe smoking in period of heaviest pipe smoking)
```{r}
summary(W1_Sam_prob_control$pipfreq2)
sd(W1_Sam_prob_control$pipfreq2)
#NA for all
```
#pipons (How old were you when you began to smoke a pipe?)
```{r}
summary(W1_Sam_prob_control$pipons)
sd(W1_Sam_prob_control$pipons)
#min: 16
#median: 18
#mean: 17.33
#max: 18
#sd: NA
```
#chwcrit (Have you ever used snuff or chewed tobacco {ALMOST EVERY DAY FOR AT LEAST A MONTH}?)
```{r}
summary(W1_Sam_prob_control$chwcrit)
sd(W1_Sam_prob_control$chwcrit)
#min: 0
#median: 0
#mean: 0.03741
#max: 1
#sd: 0.1899928
```
#chwcrit2 (Used snuff or chewed tobacco more than 5 times in your life?)
```{r}
summary(W1_Sam_prob_control$chwcrit2)
sd(W1_Sam_prob_control$chwcrit2)
#NA for all
```
#chwpeak (How many pouches of snuff/chews per day when you were using most?)
```{r}
summary(W1_Sam_prob_control$chwpeak)
sd(W1_Sam_prob_control$chwpeak)
#min: 1
#median: 2
#mean: 3.733
#max: 16
#sd: NA
```
#chwcurr (In past 12 months, how many pouches of snuff or chews used per day?)
```{r}
summary(W1_Sam_prob_control$chwcurr)
sd(W1_Sam_prob_control$chwcurr)
#NA for all
```
#chwfreq1 (Usual frequency of snuff/chew in past 12 months)
```{r}
summary(W1_Sam_prob_control$chwfreq1)
sd(W1_Sam_prob_control$chwfreq1)
#NA for all
```
#chwfreq2 (Usual frequency of snuff/chew during period of heaviest use)
```{r}
summary(W1_Sam_prob_control$chwfreq2)
sd(W1_Sam_prob_control$chwfreq2)
#NA for all
```
#chwons (How old were you when you began using tobacco or snuff?)
```{r}
summary(W1_Sam_prob_control$chwons)
sd(W1_Sam_prob_control$chwons)
#min: 11
#median: 14
#mean: 14.47
#max: 17
#sd: NA
```
**TEST Histograms
#age
```{r}
hist_W1_prob_control_age<- ggplot(W1_Sam_prob_control, aes(x=nage))+
  geom_histogram(color="darkslategrey",fill="palevioletred1") +
  facet_wrap(~nsex) +
  labs(title = "W1 CIDI-SAM Proband Control Age by Sex") +
  labs(x="Age", y="Count")
hist_W1_prob_control_age
```
#cigcrit
```{r}
hist_W1_prob_control_cigcrit<- ggplot(W1_Sam_prob_control, aes(x=cigcrit))+
  geom_histogram(color="darkslategrey",fill="palevioletred1") +
  facet_wrap(~nsex) +
  labs(title = "W1 CIDI-SAM Proband Control Cigarette Criteria by Sex") +
  labs(x="cigcrit", y="Count")
hist_W1_prob_control_cigcrit
```
#cigpeak
```{r}
hist_W1_prob_control_cigpeak<- ggplot(W1_Sam_prob_control, aes(x=cigpeak))+
  geom_histogram(color="darkslategrey",fill="palevioletred1") +
  facet_wrap(~nsex) +
  labs(title = "W1 CIDI-SAM Proband Control Cigarette Peak by Sex") +
  labs(x="cigpeak", y="Count")
hist_W1_prob_control_cigpeak
```
#cigons
```{r}
hist_W1_prob_control_cigons<- ggplot(W1_Sam_prob_control, aes(x=cigons))+
  geom_histogram(color="darkslategrey",fill="palevioletred1") +
  facet_wrap(~nsex) +
  labs(title = "W1 CIDI-SAM Proband Control Cigarette Onset by Sex") +
  labs(x="cigons", y="Count")
hist_W1_prob_control_cigons
```
#cgrcrit
```{r}
hist_W1_prob_control_cgrcrit<- ggplot(W1_Sam_prob_control, aes(x=cgrcrit))+
  geom_histogram(color="darkslategrey",fill="palevioletred1") +
  facet_wrap(~nsex) +
  labs(title = "W1 CIDI-SAM Proband Control Cigar Criteria by Sex") +
  labs(x="cgrcrit", y="Count")
hist_W1_prob_control_cgrcrit
```
#cgrpeak
```{r}
hist_W1_prob_control_cgrpeak<- ggplot(W1_Sam_prob_control, aes(x=cgrpeak))+
  geom_histogram(color="darkslategrey",fill="palevioletred1") +
  facet_wrap(~nsex) +
  labs(title = "W1 CIDI-SAM Proband Control Cigar Peak by Sex") +
  labs(x="cgrpeak", y="Count")
hist_W1_prob_control_cgrpeak
```
#cgrons
```{r}
hist_W1_prob_control_cgrons<- ggplot(W1_Sam_prob_control, aes(x=cgrons))+
  geom_histogram(color="darkslategrey",fill="palevioletred1") +
  facet_wrap(~nsex) +
  labs(title = "W1 CIDI-SAM Proband Control Cigar Onset by Sex") +
  labs(x="cgrons", y="Count")
hist_W1_prob_control_cgrons
```
#pipcrit
```{r}
hist_W1_prob_control_pipcrit<- ggplot(W1_Sam_prob_control, aes(x=pipcrit))+
  geom_histogram(color="darkslategrey",fill="palevioletred1") +
  facet_wrap(~nsex) +
  labs(title = "W1 CIDI-SAM Proband Control Pipe Criteria by Sex") +
  labs(x="pipcrit", y="Count")
hist_W1_prob_control_pipcrit
```
#pippeak
```{r}
hist_W1_prob_control_pippeak<- ggplot(W1_Sam_prob_control, aes(x=pippeak))+
  geom_histogram(color="darkslategrey",fill="palevioletred1") +
  facet_wrap(~nsex) +
  labs(title = "W1 CIDI-SAM Proband Control Pipe Peak by Sex") +
  labs(x="pippeak", y="Count")
hist_W1_prob_control_pippeak
```
#pipons
```{r}
hist_W1_prob_control_pipons<- ggplot(W1_Sam_prob_control, aes(x=pipons))+
  geom_histogram(color="darkslategrey",fill="palevioletred1") +
  facet_wrap(~nsex) +
  labs(title = "W1 CIDI-SAM Proband Control Pipe Onset by Sex") +
  labs(x="pipons", y="Count")
hist_W1_prob_control_pipons
```
#chwcrit
```{r}
hist_W1_prob_control_chwcrit<- ggplot(W1_Sam_prob_control, aes(x=chwcrit))+
  geom_histogram(color="darkslategrey",fill="palevioletred1") +
  facet_wrap(~nsex) +
  labs(title = "W1 CIDI-SAM Proband Control Chewing Tobacco Criteria by Sex") +
  labs(x="chwcrit", y="Count")
hist_W1_prob_control_chwcrit
```
#chwpeak
```{r}
hist_W1_prob_control_chwpeak<- ggplot(W1_Sam_prob_control, aes(x=chwpeak))+
  geom_histogram(color="darkslategrey",fill="palevioletred1") +
  facet_wrap(~nsex) +
  labs(title = "W1 CIDI-SAM Proband Control Chewing Tobacco Peak by Sex") +
  labs(x="chwpeak", y="Count")
hist_W1_prob_control_chwpeak
```
#chwons
```{r}
hist_W1_prob_control_chwons<- ggplot(W1_Sam_prob_control, aes(x=chwons))+
  geom_histogram(color="darkslategrey",fill="palevioletred1") +
  facet_wrap(~nsex) +
  labs(title = "W1 CIDI-SAM Proband Control Chewing Tobacco Onset by Sex") +
  labs(x="chwons", y="Count")
hist_W1_prob_control_chwons